We need to beat namespotting, no idea how

### 2023-01-30 paperSubmission/paperSubmission1.tex
small changes

>>>>

\section{Collective Intelligence and  moderation}\label{collective-intelligence-approach-to-counter-speech}

The main objective of the experiment was to test whether the level of verbal aggression (personal attacks) of a group of users regularly attacking others on Reddit can be significantly decreased by community-driven, counter-speech interventions conducted by volunteers in partnership with Artificial Intelligence (collective intelligence approach).

Verbal aggression was defined in this experiment as a personal attack---any kind of verbal harassment, insult, or threat directed against the interlocutor in a text-based conversation online. Those were detected using Samurai Labs' cyberviolence detection system, describe in detail in Section \ref{sec:technology}.

Traditionally, collective intelligence has been defined as "a group or a team's combined capacity and capability to perform a wide variety of tasks and solve diverse problems" \citep{woolley2015collective}. In our paper and in the theoretical underpinnings of the experiment itself, we will be relying on a collective intelligence scope proposed by Nesta, an innovation foundation (\url{https://www.nesta.org.uk}), which focuses on a collaboration between human and machine intelligence to develop innovative solutions to social challenges.

Instead of using a negative motivation system, the assumption was to test a positive one—convincing verbally violent users to refrain from using cyberviolence based on civic education—peer-pressure regulation and experiential learning of a positive set of norms and empathy. Algorithms developed for the detection of personal attacks were used to monitor the activity of experimental groups and notify volunteers about all attacks generated by its members. Volunteers, after receiving a notification on Slack, could then react with a proper intervention. Such an approach served as a distributed bottom-up voluntary model of moderation based on collective intelligence—utilizing human + machine intelligence to develop solutions to social challenges.

Normative interventions can refer either to general social norms of civility and respect, community standards, a particular subreddit rule, or a descriptive norm among others. Empathetic interventions can refer to the emotional state of the recipient or the sender of the attack or both. They are designed to evoke an empathetic response. Here are some examples of interventions that were used during the experiment: 
\begin{itemize}
  \item \emph{Insulting others is against Reddit's policy.} (normative)
  \item \emph{Hey there, we do not call each other like that here.} (normative)
  \item \emph{There is a human being on the other side who might be hurt by your words.} (empathetic)
  \item \emph{I see you are frustrated but remember the human.} (empathetic)
\end{itemize}

Our hypotheses were as follows:

\vspace{2mm}

\begin{tabular}{lp{11cm}}
H1 & If a group of human volunteers, notified by an AI-based 
detection system about verbal aggression generated by the treatment group users, responds with counter-speech interventions, this will result in a decreased verbal aggression level for the whole group after the intervention period.\\
H2 &  If two groups receive different types of interventions (empathy-based or normative), then the decrease in verbal aggression will be larger in the case of normative interventions in comparison to the empathy-based ones. 
\end{tabular}

%the reasoning behind H2
Although empathy has been found to be helpful in the reduction of aggressive behavior \citep{bjorkqvist2000social}, and the improvement of intergroup relations \citep{stephan1999role}, there are also important arguments and evidence concerning its limits. Specifically, Paul Bloom in his book \emph{}Against Empathy: The Case for Rational Compassion} \citep{bloom2017against}, stresses that empathy can have a very narrow focus and can be prone to biases. For instance, it’s easier to be empathetic towards those who are close or similar to us. Since conversations on Reddit are anonymous and usually occur between strangers, we expected  empathetic interventions to  be less effective than normative interventions in curbing personal attacks.
